% -*- program: xelatex -*-


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout
\hfuzz=20pt
\vfuzz=29pt
\hbadness=20000
\vbadness=\maxdimen

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Mark Arts -- Resume} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> Elizabeth Wolffstraat 7-1,\\ % Address line 1
\> Amsterdam, 1052RN \\ % Address line 2
{\bf Date of Birth} \> 6$^{th}$ April 1993 \\ % Date of birth
{\bf Nationality} \> Dutch \\% Nationality
{\bf Mobile Phone} \> +31627139646 \\ % Mobile phone
{\bf Email} \> \href{mailto:marktarts93@gmail.com}{marktarts93@gmail.com} \\ % Email address
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}

A passionate and curious programmer with a broad skill set looking for a position where he can utilize and learn interesting technologies and tools. \\

I started programming for my bachelor and quickly decided to combine my studies with work to learn not only how to quickly build small projects but also what it means to write in an professional context. Trying to keep myself challenged I learned various languages, with a focus on functional programming. \\

Besides web-development and DevOps I enjoy reading and learning about Artificial Intelligence, security / hacking, game development, psychology, Blockchains and other software related subjects. \\

Next to being a programmer I enjoy making music and learning about sound design, being able to play and use multiple acoustic and digital instruments. \\

I'm a fast and enthusiastic learner that is always up for a new challenge.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
  \bf{2010-2017} \> BSc in Media Technology - \href{https://www.rotterdamuas.com}{Rotterdam University of Applied Sciences} \\[5pt]
  \>Minor in Game Design and Development \\[5pt]
  \>Thesis: How can we realise a digital environment in which non-programmers, like 3D \\ \> modellers and level designers, can build a efficiënt and uniqe Virtual Reality experience
}

%------------------------------------------------

\tabbedblock{
  \bf{2005-2010} \> Higher General Secondary Education - Emmauscollege, Rotterdam\\[5pt]
}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{May 2017 -}{Now}
{GUTS / GET-protocol, Amsterdam, Netherlands}
{http://guts.tickets}
{DevOps / Developer}
{As the only DevOps engineer at GUTS I was responsible for the creation and maintenance of the infrastructure of the GUTS ticketing system which at point of writing consisted of multiple services spread and balanced over multiple linux servers and lambda's in AWS. My tasks also included creating and maintaining our internal tooling including Gitlab, CI (continues integration / testing), metric / log aggregation and visualization, error reporting, backups and other. Next to my DevOps work i worked as both a Back and Front-end developer when our planning allowed it.

\rule{0mm}{5mm}\textbf{Technologies:} Linux, Python, Go (golang), Ansible, Terraform, Django, Docker, Vue, AWS, Azure, Sentry, ELK, Grafana, Nix, Docker, Gitlab }

\job
{Aug 2016 -}{May 2017}
{Hoppinger, Rotterdam, Netherlands}
{http://www.hoppinger.com}
{DevOps / Developer}
{After my graduation internship I returned to working at Hoppinger while finishing my study. In this year I started focusing more on building automation for DevOps and server management through Puppet

\rule{0mm}{5mm}\textbf{Technologies:} Puppet, Bash, PHP, Ruby, Rails, Wordpress, Nix, Docker, Gulp, Linux, Apache, NGINX }

\job
{Feb 2016 -}{Jun 2016}
{DPI, Den Haag, Netherlands}
{http://www.dpi.com}
{Graduation Internship}
{I researched the possibility for 3D studio's to create interactive VR stories without the need of a programmer in the Unreal Engine utilizing its visual scripting system Blueprints.\\
\rule{0mm}{5mm}\textbf{Technologies:} Unreal Engine 4, Blueprints, C++, Virtual Reality}

\job
{Feb 2013 -}{Feb 2016}
{Hoppinger, Rotterdam, Netherlands}
{http://www.hoppinger.com}
{Internship / working student}
{After my internship at Hoppinger I stayed to reinforce the service and support team. As a service and support member I was responsible for the maintenance and small feature requests for Wordpress, Rails and Drupal projects. When I was available full-time, for example vacations, I worked on building bigger projects.

\rule{0mm}{5mm}\textbf{Technologies:} PHP, Ruby, Javascript, Sass, Less, Python, Erb, Haml, Wordpress. Ruby on Rails, NodeJS, Puppet, Drupal, Gulp, Drush, Composer, NGINX, Apache, Git, Polymer, React, MySQL, PostgreSQL, Elasticsearch
}

\job
{Jul 2012 -}{Aug 2012}
{Unitas, Rotterdam, Netherlands}
{http://www.unitas.nl}
{Junior Developer}
{In the summer after the second year of my bachelor I worked for a company that created a software package to submit import and export request to the dutch customs.

\rule{0mm}{5mm}\textbf{Technologies:} WinDev, EDIFACT
}

%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Software Engineering Skills}

\skillgroup{Programming Languages in production}
{
\textit{Python}\\
\textit{Go}\\
\textit{Ruby}\\
\textit{Terraform}\\
\textit{PHP}\\
\textit{C++}\\
\textit{C\#}\\
\textit{Javascript}\\
\textit{Bash} - Server scripting / automation
}

\skillgroup{Programming Languages in hobby projects}
{
  \textit{Haskell}\\
  \textit{Java}\\
  \textit{Typescript}\\
  \textit{Lisp}\\
  \textit{Lua} \\
  \textit{Clojure}\\
}

%------------------------------------------------

\skillgroup{Web Development}
{
\textit{HTML5, HAML / TWIG / SLIM / ERB, CSS3/SASS/LESS}\\
\textit{Django, Ruby on Rails, Wordpress, Drupal}\\
\textit{Apache/Nginx, UNIX systems, AWS, Azur Lambdas, CDN's}\\
}

%------------------------------------------------

\skillgroup{Miscellaneous}
{
\textit{Puppet}\\
\textit{Docker}\\
\textit{Gulp/Grunt}\\
\textit{git}\\
\textit{NixOS/Docker}\\
}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\interestsgroup{
 \interest{Running, Cycling, Yoga}
 \interest{Music, Composing, Producing, Sound design, Piano, Accordion, Guitar, Modular Synthesizers}
}

\end{document}